---
title: "Untitled"
author: '9240'
date: "08/05/2022"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, results='hide', message=FALSE, warning=FALSE}
# imports
library(rpart)
library(caret)
library(ggplot2)
library(Rtsne)
library(dplyr)
library(tidyr)
library(corrplot)
library(cluster)
library(pheatmap)
library(factoextra)
library(FactoMineR)
library(mclust)
# library(e1071) # provides soft clustering algos
library(tidyr)
# library(data.table)
library(dbscan)
library(fpc)
# library(RANN)
library(TSclust)
set.seed(42)
```


# Algorithm
- create NxN similarity matrix
- for each TS var:
      - calculate similarity matrix based on a distance measure
      - append to main similarity matrix
- divide similarity matrix my len(vars)
- produce network graph
- cluster graph

```{r}
#' Clustering Using Custom Algo
#'
#' @param vars 
#' @param incomes 
#' @param k 
#' @param metric 
#'
#' @return Confusion Matrix Statistics and Computed Classes
#' @export
#'
#' @examples
cluster_custom <- function(vars, incomes, k, metric, dataset) {
  
  # Load data
  data <- read.csv(file=paste("./data/", dataset, sep=""))
  x_diss = NA
  x_diss_2 = NA
  actual_incomes = 0
  iso_order <- 0
  
  tot <- NA
  tot_2 <- NA
  first_run <- TRUE
  
  for (var in vars) {
    x <- data[data$varnum == var,]
    
    # standardise
    x$median <- scale(x$median)
    
    # select income groups to analyse
    x <- x[x$income %in% c('1','3'),]
    
    x <- x[c('iso3', 'year', 'median')]
    
    # reshape
    x <- reshape(x, idvar = "iso3", timevar="year", direction = "wide")
    rownames(x) <- x$iso3
    x <- x[,c('median.1990', 'median.1995', 'median.2000', 'median.2005', 'median.2010', 'median.2015', 'median.2018')]
  
    iso_order <- rownames(x)
    x <- as.matrix(sapply(x, as.numeric))
    
    # calc dissimilarity
    x_diss <- diss(x, metric)
    x_diss_2 <- x_diss
    x_diss <- as.matrix(x_diss)
    
    if (first_run) {
      tot <- x_diss
      tot_2 <- x_diss_2
      first_run <- FALSE
    } else {
      tot <- tot + x_diss
      tot_2 <- tot_2 + x_diss_2
    }
  }
  
  # apply PAM clustering
  pam.res <- pam(tot, k)
  resc <- pam.res$clustering
  resc <- as.data.frame(resc)
  rownames(resc) <- iso_order
  
  # apply hierarchical clustering
  clusters <- hclust(tot_2, method="ward.D")
  # plot(clusters)
  hclabels <- cutree(clusters, k=2)

  # retrieve actual income values
  resc$income <- NA
  for(country in rownames(resc)) {
     resc[country,]$income <- data[data$iso3==country,]$income[1]
  }
  resc[resc$income==3,]$income <- 2
  
  resc$not_equal <- NA
  resc$not_equal <- resc$resc==resc$income
  
  # results
  confusionMatrix(as.factor(resc$resc), as.factor(resc$income))$overall['Accuracy']
  cf <- confusionMatrix(as.factor(resc$resc), as.factor(resc$income))
  resList <- list("cf" = cf, "df" = resc, "hclabels"=as.factor(hclabels), "truth"=as.factor(resc$income))
  return(resList)
}
```

Run This
Common in rich countries: 15, 54
```{r}
test_res <- cluster_custom(c(100, 6), c(1, 3), 2, "CORT", "data_female_0.csv")

# PAM
source("utils.R", local = knitr::knit_global())
# get_results(as.factor(test_res$df$resc), as.factor(test_res$truth))

# hclust
print("hclust")
get_results(test_res$hclabels, as.factor(test_res$truth))
```

```{r}
a <- get_results(test_res$hclabels, as.factor(test_res$truth))
```


# Test out different metrics
```{r}
source("utils.R", local = knitr::knit_global())

metrics <- c("ACF", "AR.PIC", "CDM", "COR", "CORT", "DTWARP", "EUCL", "INT.PER", "NCD", "PACF", "PER")

cluster_results <- c()

# initial a df for results
df <- data.frame(
  "Algo"= character(),
  "Distance Metric"= character(),
  "Sub Clustering Algo"=character(),
  "Dataset"=character(),
  "Accuracy"=numeric(),
  "Sensitivity"=numeric(),
  "Specificity"=numeric(),
  "Rand Index"=numeric(),
  "Adj Rand Index"=numeric()
)

for (dataset in c("female_0", "female_1", "all_999")) {
  for (metric in metrics) {
    res <- cluster_custom(c(100, 6), c(1, 3), 2, metric, paste("data_", dataset, ".csv", sep="")) 
    print(metric)
    
    # first PAM
    res_pam <- get_results(as.factor(res$df$resc), as.factor(res$truth))
    df[nrow(df)+1,] <- c(
      "Custom", 
      metric, 
      "PAM", 
      dataset, 
      res_pam$cfm$overall['Accuracy'], 
      res_pam$cfm$byClass['Sensitivity'], 
      res_pam$cfm$byClass['Specificity'], 
      res_pam$ri,
      res_pam$ari
    )
    
    # repeat for HClust
    res_hclust <- get_results(res$hclabels, as.factor(res$truth))
    df[nrow(df)+1,] <- c(
      "Custom", 
      metric, 
      "HCLUST",
      dataset,
      res_hclust$cfm$overall['Accuracy'],
      res_hclust$cfm$byClass['Sensitivity'],
      res_hclust$cfm$byClass['Specificity'],
      res_hclust$ri,
      res_hclust$ari
    )
  }
}

df_ordered <- df[order(df$Distance.Metric, df$Sub.Clustering.Algo, df$Dataset),]
```

High acc: ncd, eucl, dtwarp, cort, cdm



# Now try with clustering code inside package
```{r}
source("utils.R", local = knitr::knit_global())
source("./customcluster/R/hello.R", local = knitr::knit_global())
data <- select_data("all_999", c(1, 2, 3), c(100, 6))
```

```{r}
result <- customcluster(data, k=2, cluster_algo="HCLUST")
get_results(result$result, result$income)
```


```{r}
source("./customcluster/R/hello.R", local = knitr::knit_global())
data <- select_data("all_999", c(3, 6), c(100, 6, 4, 5, 2, 5))
result <- customcluster(data, k=2, cluster_algo="PAM", dist_metric="")

print(result$income)

get_results(result$result, result$income)
```
1, 6 good
3, 6 bad
1, 2, 3 
```{r}
source("utils.R", local = knitr::knit_global())

metrics <- c("ACF", "AR.PIC", "CDM", "COR", "CORT", "DTWARP", "EUCL", "INT.PER", "NCD", "PACF", "PER")

cluster_results <- c()

# initial a df for results
df <- data.frame(
  "Algo"= character(),
  "Distance Metric"= character(),
  "Sub Clustering Algo"=character(),
  "Dataset"=character(),
  "Accuracy"=numeric(),
  "Sensitivity"=numeric(),
  "Specificity"=numeric(),
  "Rand Index"=numeric(),
  "Adj Rand Index"=numeric()
)

for (dataset in c("all_999")) {
  print(dataset)
  data <- select_data(dataset, c(1, 2, 3), c(100, 6))
  for (metric in metrics) {
    print(metric)
    res <- customcluster(data, k=3, cluster_algo="PAM", dist_metric=metric)
    res_pam <- get_results(res$result, res$income)
    print(res_pam$cfm$overall['Accuracy'])
    df[nrow(df)+1,] <- c(
      "Custom", 
      metric, 
      "PAM", 
      dataset, 
      res_pam$cfm$overall['Accuracy'], 
      res_pam$cfm$byClass['Sensitivity'], 
      res_pam$cfm$byClass['Specificity'], 
      res_pam$ri,
      res_pam$ari
    )
  }
}

df_ordered <- df[order(df$Distance.Metric, df$Sub.Clustering.Algo, df$Dataset),]
```

