---
title: "Untitled"
author: '9240'
date: "08/05/2022"
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(flextable)
library(dplyr)
library(officer)
DIR <- "./results/"
source("utils.R", local = knitr::knit_global())
source("./customcluster/R/hello.R", local = knitr::knit_global())
```

```{r}
set_flextable_defaults(
  font.family = "CMU Serif",
  font.size = 10,
  font.color = NULL,
  text.align = NULL,
  padding = NULL,
  padding.bottom = NULL,
  padding.top = NULL,
  padding.left = NULL,
  padding.right = NULL,
  border.color = NULL,
  background.color = NULL,
  line_spacing = NULL,
  table.layout = NULL,
  cs.family = NULL,
  eastasia.family = NULL,
  hansi.family = NULL,
  decimal.mark = NULL,
  big.mark = NULL,
  digits = NULL,
  na_str = NULL,
  nan_str = NULL,
  fmt_date = NULL,
  fmt_datetime = NULL,
  extra_css = NULL,
  fonts_ignore = NULL,
  theme_fun = NULL,
  post_process_pdf = NULL,
  post_process_docx = NULL,
  post_process_html = NULL,
  post_process_pptx = NULL
)
```

# Setup results

```{r}
configs <- list(
    list(
    Incomes = c(1,2,3),
    VariableRepeats = c(15, 35, 38, 43, 54),
    Datasets = c("all_999", "female_0", "female_1")
  ),
  list(
    Incomes = c(1,3),
    VariableRepeats = c(15, 35, 38, 43, 54),
    # sugar sweetened beverages, added sugar, iodine, vitamin A, zinc 
    Datasets = c("all_999", "female_0", "female_1")
  ),
  list(
    Incomes = c(1,6),
    VariableRepeats = c(15, 35, 38, 43, 54),
    Datasets = c("all_999", "female_0", "female_1")
  )
)
```

```{r}
add_row <- function(df, algo, metric, dataset, variable, incomes, time.taken, stats) {
  print(paste(algo, metric, dataset, variable, time.taken, stats$cfm$overall[['Accuracy']]))
  df[nrow(df)+1,] <- c(
    algo, 
    metric,
    dataset, 
    variable,
    toString(incomes),
    time.taken,
    stats$cfm$overall['Accuracy'], 
    stats$cfm$byClass['Sensitivity'], 
    stats$cfm$byClass['Specificity'], 
    stats$ri,
    stats$ari
  )
  return(df)
}
```

# Run all results

```{r}
# for (config in configs) {
#   print(config$Incomes)
# }

run_config <- function(config) {
  df <- data.frame(
    "Algo"= character(),
    "Distance Metric"= character(),
    "Dataset"=character(),
    "Variable"=character(),
    "Incomes"=character(),
    "Time.Taken"=numeric(),
    "Accuracy"=numeric(),
    "Sensitivity"=numeric(),
    "Specificity"=numeric(),
    "Rand Index"=numeric(),
    "Adj Rand Index"=numeric()
  )

  k = length(config$Incomes)
  for (variable in config$VariableRepeats) {
    for (dataset in config$Datasets) {
      data <- select_data(dataset, config$Incomes, c(100, variable))
      
      algo = "DTWCLUST"
      metric = "N/A"
      start.time <- Sys.time()
      result <- clusterdtw(data, k=k)
      end.time <- Sys.time()
      time.taken <- end.time - start.time
  
      stats <- get_results(result$result, result$income)
      df <- add_row(df, algo, metric, dataset, variable, toString(config$Incomes), time.taken, stats)
  
      custom_metrics <- c("CDM", "CORT", "DTWARP", "EUCL", "NCD")
      
      algo = "Custom PAM"
      for (metric in custom_metrics) {
        start.time <- Sys.time()
        result <- customcluster(data, k=k, cluster_algo="PAM", dist_metric=metric)
        end.time <- Sys.time()
        time.taken <- end.time - start.time
        stats <- get_results(result$result, result$income)
        df <- add_row(df, algo, metric, dataset, variable, toString(config$Incomes), time.taken, stats)
      }
      
      # for (metric in custom_metrics) {
      #   result <- customcluster(data, k=k, cluster_algo="HCLUST", dist_metric=metric)
      #   stats <- get_results(result$result, result$income)
      #   df <- add_row(df, algo, metric, dataset, variable, stats)
      # }
    }
  }
  return(df)
}


df_tot <- NA
for (config in configs) {
  x <- run_config(config)
  if (!is.na(df_tot)) {
    df_tot <- rbind(df_tot, x)
  }
}
```

```{r}
write.csv(df_tot, paste(DIR, "results.csv", sep=""))
```

```{r}
df_all <- read.csv(file =paste(DIR, "results.csv", sep=""))

df_grouped <- df_all %>%
  group_by(across(all_of(c("Algo", "Distance.Metric", "Dataset", "Incomes")))) %>%
  summarise(Mean.Accuracy = mean(Accuracy))

Mean.Time <- df_all%>%
  group_by(across(all_of(c("Algo", "Distance.Metric", "Dataset", "Incomes")))) %>%
  summarise(Mean.Time = mean(Time.Taken))


Mean.Sensitivity <- df_all%>%
  group_by(across(all_of(c("Algo", "Distance.Metric", "Dataset", "Incomes")))) %>%
  summarise(Mean.Sensitivity = mean(Sensitivity))


Mean.Specificity <- df_all%>%
  group_by(across(all_of(c("Algo", "Distance.Metric", "Dataset", "Incomes")))) %>%
  summarise(Mean.Specificity = mean(Specificity))

Mean.Rand.Index <- df_all%>%
  group_by(across(all_of(c("Algo", "Distance.Metric", "Dataset", "Incomes")))) %>%
  summarise(Mean.Rand.Index = mean(Rand.Index))

Mean.Adj.Rand.Index <- df_all%>%
  group_by(across(all_of(c("Algo", "Distance.Metric", "Dataset", "Incomes")))) %>%
  summarise(Mean.Adj.Rand.Index = mean(Adj.Rand.Index))

df_grouped$Mean.Time <- Mean.Time$Mean.Time
df_grouped$Mean.Sensitivity <- Mean.Sensitivity$Mean.Sensitivity
df_grouped$Mean.Specificity <- Mean.Specificity$Mean.Specificity
df_grouped$Mean.Rand.Index <- Mean.Rand.Index$Mean.Rand.Index
df_grouped$Mean.Adj.Rand.Index <- Mean.Adj.Rand.Index$Mean.Adj.Rand.Index

```

```{r}
df_all
```

# Format table

```{r}
df_export <- df_grouped[df_grouped$Distance.Metric %in% c("N/A", "EUCL"),]
df_export <- df_export[order(df_export$Incomes, df_export$Algo, df_export$Dataset),]

ft <- flextable(df_export)
ft <- font(ft, fontname="CMU Serif", part="all")
ft <- font(ft, fontname="CMU Serif BOLDONLY", part="header")
ft <- border(ft, border=fp_border(color="black"), part="all")
ft <- colformat_double(ft, digits = 3, na_str = "N/A")

ft <- padding(
  ft, 
  padding.top = 0,
  padding.bottom = 0,
  padding.left = 2,
  padding.right = 2,
  part = "all"
)

ft <- padding(
  ft, 
  padding.top = 0,
  padding.bottom = 0,
  padding.left = 2,
  padding.right = 2,
  part = "header"
)

ft <- padding(
  ft, 
  padding.top = 0,
  padding.bottom = 0,
  padding.left = 2,
  padding.right = 2,
  part = "body"
)

ft <- line_spacing(ft, space = 1, part = "all")

ft <- align(ft, align="center", part="all")
# ft <- autofit(ft)
ft
```

```{r}
save_as_docx(ft, path=paste(DIR, "mean.docx", sep=""))
```

```{r}
a <- colnames(df_export) 
gsub("//.", " ", a)
```


# Caclulate Reference / Expected Values

2 classes

```{r}


simulate_reference <- function(classes, class_size, repeats){
  truth <- rep(1:classes, each=class_size)
  table(truth)

  acc_count = c()
  rand_count = c()
  adj_rand_count = c()
  for (i in 1:repeats) {
    set.seed(i)
    # generate random pred
    x <- sample(x = c(1:classes), size=class_size*classes, replace = TRUE)
    
    # calculate acc from get_results
    res <- get_results(x, truth)
    
    #print(res$cfm$overall[['Accuracy']])
    # add to current count
    #acc_count <- acc_count + res$cfm$overall[['Accuracy']]
    acc_count <- append(acc_count, as.numeric(res$cfm$overall[['Accuracy']]))
    rand_count <- append(rand_count, as.numeric(res$ri))
    adj_rand_count <- append(adj_rand_count, as.numeric(res$ari))
  }
  
  return(list("accuracy"=acc_count, "rand"=rand_count, "adj_rand"=adj_rand_count))
}

sim3 <- simulate_reference(classes=3, class_size=50, repeats=1000)
```

```{r}
sim2 <- simulate_reference(classes=2, class_size=50, repeats=1000)
```

```{r}
plot_dist <- function(sim_res, n_classes) {
  C1 <- data.frame(value=sim_res$accuracy, variable = "Accuracy")
  C2 <- data.frame(value=sim_res$rand, variable = "Rand")
  C3 <- data.frame(value=sim_res$adj_rand, variable = "Adj Rand")
  dat <- rbind(C1, C2, C3)
  head(dat)
  
  ggplot(dat, aes(x = variable, y = value)) +
    geom_violin()
}

plot_dist(sim3, 3)
```

```{r}
plot_dist(sim2, 2)
```

```{r}
df_sims <- data.frame(
  Number.Classes=character(),
  Median.Accuracy=numeric(), 
  Median.Rand.Index=numeric(), 
  Median.Adj.Rand.Index=numeric()
) 

df_sims[nrow(df_sims) + 1,] = c(2, median(sim2$accuracy), median(sim2$rand), median(sim2$adj_rand))
df_sims[nrow(df_sims) + 1,] = c(3, median(sim3$accuracy), median(sim3$rand), median(sim3$adj_rand))

ft <- flextable(df_sims)
ft <- font(ft, fontname="CMU Serif", part="all")
ft <- font(ft, fontname="CMU Serif BOLDONLY", part="header")
ft <- border(ft, border=fp_border(color="black"), part="all")
ft <- colformat_double(ft, digits = 3, na_str = "N/A")

ft <- padding(
  ft, 
  padding.top = 0,
  padding.bottom = 0,
  padding.left = 2,
  padding.right = 2,
  part = "all"
)

ft <- padding(
  ft, 
  padding.top = 0,
  padding.bottom = 0,
  padding.left = 2,
  padding.right = 2,
  part = "header"
)

ft <- padding(
  ft, 
  padding.top = 0,
  padding.bottom = 0,
  padding.left = 2,
  padding.right = 2,
  part = "body"
)

ft <- line_spacing(ft, space = 1, part = "all")

ft <- align(ft, align="center", part="all")
# ft <- autofit(ft)
ft
```

```{r}
save_as_docx(ft, path=paste(DIR, "reference_vals.docx", sep=""))
```

  # TODO: make formatting a function, replace . in colnames with space

# Attempt DTWclust tuning

create tuning grid


```{r}
library(tidyr)
grid <- crossing(
  norm = c("L1", "L2"),
  sqrt.dist = c(TRUE, FALSE),
  backtrack = c(TRUE, FALSE),
  normalize = c(TRUE, FALSE)
)
```

# Tune DTW

```{r}
res <-  data.frame(
  params=character(),
  i_n=integer(),
  j=integer(),
  accuracy=numeric()
)

data <- select_data("all_999", c(1,2,3), c(100, 15))

print("number of combinations:")
print(nrow(grid))
  
  
i_n <- 1 # param id           
for (i in 1:nrow(grid)) {
  row <- grid[i,]
  for (j in 1:1000) {
    # 1000 repeats each (change seed)
    
    result <- clusterdtw(data, k=3, normalize=row$normalize, norm=row$norm, sqrt.dist=row$sqrt.dist, backtrack=row$backtrack, seed=j)
    stats <- get_results(result$result, result$income)
    
    # collate accuracies
    
    res[nrow(res) + 1,] = c(paste(row, collapse=" "), i_n, j, stats$cfm$overall[['Accuracy']])
  }
  print(row)
  i_n = i_n + 1
}
```

```{r}
for (i in 0:15){
  print(paste0("Combo:", i+1))
  print(as.character(res[i*1000+3,]['params']))
}
# 1-4 what is changing is uninportant: backtrack, normalisation
# 5-8 unimpotant: same
```

```{r}
library(ggplot2)
  
res2 <- res[,c('i_n', 'accuracy')]
res2$ParameterCombination <- as.factor(as.numeric(res2$i_n))
res2$Accuracy <- as.numeric(res2$accuracy)
p <- ggplot(res2, aes(x=ParameterCombination, y=Accuracy)) + 
  geom_violin()
p <- p + stat_summary(fun.y=median, geom="point", size=2, color="red")
p
```
```{r}
as.factor(as.numeric(res2$i_n))
```

```{r}
library(ggplot2)
ggsave(
  paste(DIR, "tuning.png", sep=""),
  plot = p,
)
```

Print median values for each

```{r}
res3 <- res2[,c('Accuracy', 'ParameterCombination')]
library(dplyr)
res4 <- res3 %>%
  group_by(ParameterCombination)%>% 
  summarise(Mean=mean(Accuracy), Max=max(Accuracy), Min=min(Accuracy), Median=median(Accuracy), Std=sd(Accuracy))

res4
```

```{r}
grid[6,]
```

Normalise no effect

```{r}
grid[7,]
```

Backtrack no effect

```{r}
grid[8,]
```

```{r}
grid[14,]
```

# map plots

iso coverage (incomes, 1,2,3,6), colored

```{r}
data <- select_data("all_999", c(1,2,3,6), c(15))
data <- data[,c("iso3", "income")]
data <- data[!duplicated(data), ]

library(rworldmap)

## Create multiple color codes, with Burkina Faso in its own group
malDF <- data.frame(
  country = c("DEU", "COD", "BFA"),
  malaria = c(1, 1, 2)
)

## Re-merge
malMap <- joinCountryData2Map(
  data, 
  joinCode = "ISO3",
  nameJoinColumn = "iso3"
)

## Specify the colourPalette argument
mapCountryData(
  malMap, 
  nameColumnToPlot="income", 
  catMethod = "categorical",
  missingCountryCol = gray(.8), 
  colourPalette = c("red", "blue", "green", "yellow"),
  addLegend = TRUE
)
```

create function to plot these for cluster results

```{r}
plot_map <- function(result) {
  ## Re-merge
  malMap <- joinCountryData2Map(
    result, 
    joinCode = "ISO3",
    nameJoinColumn = "iso3"
  )
  
  cols <- c("red", "green", "blue", "purple")
  if (6 %in% result$result) {
    cols <- c("red", "green", "blue", "purple", "yellow", "orange")
  }
  ## Specify the colourPalette argument
  mapCountryData(
    malMap, 
    nameColumnToPlot="result", 
    catMethod = "categorical",
    missingCountryCol = gray(.8), 
    colourPalette = cols
  )
}
```

# line plots
```{r, fig.width=100,fig.height=11}
plot_lines <- function(df, colour_col='cluster', ylim=1200, black=FALSE, yaxis, key_title="clusters") {
  clusters <- as.factor(df[[colour_col]])
  years <- unique(df$year)
  
  p <- ggplot(data=df, aes(x=year, y=median, group=iso3, colour=clusters)) +
  geom_line(alpha=0.2) +
  ylim(0,ylim) +
  theme_bw() +
  guides(color = guide_legend(override.aes = list(size = 4, alpha=1))) +
  labs(color=key_title) +
  scale_x_continuous("Year", labels = as.character(years), breaks=(years)) +
  theme(text = element_text(size=15)) +
  theme(axis.title = element_text(size = 18)) +
  ylab(yaxis)

  if (black) {
    p <- p + scale_color_manual(values=c("#000000", "#000000"))
    p <- p + theme(legend.position = "none")
  }
  p
}
```

```{r}
plot_lines(data2)
```


# Do all plots

```{r}
do_all_plots <- function(result, data, varnums=c(15), income=FALSE) {
  print(table(result$result))
  
  # map plot
  print(plot_map(result))
  
  # for each varnum
  for (varnum in varnums) {
        yaxis = NULL
    if (varnum == 15){
      yaxis = "Median sugar-sweetened\nbeverage intake (g/day)"
    } else if (varnum == 100) {
      yaxis = "Nutritional deficiency\n(DALYs)"
    }
        
    ylim <- 1200
    if (varnum == 100) {
      ylim <- 0.10655375
    }
    # prepare TS data
    data2 <- data[data$varnum==varnum,]

    data2$cluster <- FALSE
    for (row in 1:nrow(result)) {
      data2[data2$iso3==(result[row,]$iso3),]$cluster <- result[row,]$result
    }
    
    # full line plot
    print(plot_lines(data2, ylim=ylim, yaxis=yaxis))
    
    # separated line plots
    for (i in 1:4) {
     print(plot_lines(data2[data2$cluster==i,], ylim=ylim, black=TRUE, yaxis=yaxis))
    }
  }
}

# do_all_plots(result, data, varnums=c(15, 100))
```

```{r}
params_opt <- grid[5,]
params_opt
```

# Apply to data | DTW

```{r}
library(tibble)
```

```{r}
data <- select_data("all_999", c(1,2,3,6), c(100, 15))
result <- clusterdtw(data, k=4, norm=params_opt$norm, sqrt.dist=params_opt$sqrt.dist)

result <- tibble::rownames_to_column(result, "iso3")
result
```

```{r}
do_all_plots(result, data, varnums=c(15,100))
```

# Apply to data | Custom

```{r}
data <- select_data("all_999", c(1,2,3,6), c(100, 15))

result <- customcluster(data, k=4, cluster_algo="PAM")
result <- tibble::rownames_to_column(result, "iso3")
result
```

```{r}
do_all_plots(result, data, varnums = ums=c(15,100))
```
# Applied 2 var, custom, cort
```{r}
data <- select_data("all_999", c(1,2,3,6), c(100, 15))

result <- customcluster(data, k=4, cluster_algo="PAM", dist_metric="CORT")
result <- tibble::rownames_to_column(result, "iso3")
result
```

```{r, fig.width=6, fig.height=3}
do_all_plots(result, data, varnums=c(15,100))
```
## Male

```{r}
data <- select_data("female_0", c(1,2,3,6), c(100, 15))

result <- customcluster(data, k=4, cluster_algo="PAM", dist_metric="CORT")
result <- tibble::rownames_to_column(result, "iso3")
```

```{r, fig.width=6, fig.height=3}
do_all_plots(result, data, varnums=c(15,100))
```

## Female

```{r}
data <- select_data("female_1", c(1,2,3,6), c(100, 15))

result <- customcluster(data, k=4, cluster_algo="PAM", dist_metric="CORT")
result <- tibble::rownames_to_column(result, "iso3")
# remap
# green to blue (2 - 5 - 3)
# blue to red (3 - 6 - 1)
# red to green (1 - 7 - 2)
result$result[result$result==2] = 5
result$result[result$result==3] = 6
result$result[result$result==1] = 7

result$result[result$result==5] = 3
result$result[result$result==6] = 1
result$result[result$result==7] = 2

result
```

```{r, fig.width=6, fig.height=3}
do_all_plots(result, data, varnums=c(15,100))
```

## Age 12.5

```{r, fig.width=6, fig.height=3}
data <- select_data("age_12.5", c(1,2,3,6), c(100, 15))

result <- customcluster(data, k=4, cluster_algo="PAM", dist_metric="CORT")
result <- tibble::rownames_to_column(result, "iso3")
# result$result[result$result==2] = 5
# result$result[result$result==3] = 6
# result$result[result$result==1] = 7
# 
# result$result[result$result==5] = 3
# result$result[result$result==6] = 1
# result$result[result$result==7] = 2

do_all_plots(result, data, varnums=c(15,100))
```


## Age 82.5
```{r, fig.width=6, fig.height=3}
data <- select_data("age_12.5", c(1,2,3,6), c(100, 15))

result <- customcluster(data, k=4, cluster_algo="PAM", dist_metric="CORT")
result <- tibble::rownames_to_column(result, "iso3")
do_all_plots(result, data, varnums=c(15,100))
```

## Edu 0
```{r, fig.width=6, fig.height=3}
data <- select_data("edu_1", c(1,2,3,6), c(100, 15))

result <- customcluster(data, k=4, cluster_algo="PAM", dist_metric="CORT")
result <- tibble::rownames_to_column(result, "iso3")
do_all_plots(result, data, varnums=c(15,100))
```



## Edu 2
```{r, fig.width=6, fig.height=3}
# data <- select_data("edu_3", c(1,2,3,6), c(100, 15))
# 
# result$result[result$result==2] = 5
# result$result[result$result==3] = 6
# result$result[result$result==1] = 7
# 
# result$result[result$result==5] = 3
# result$result[result$ result==6] = 1
# result$result[result$result==7] = 2
# 
# result <- customcluster(data, k=4, cluster_algo="PAM", dist_metric="CORT")
# result <- tibble::rownames_to_column(result, "iso3")
# do_all_plots(result, data, varnums=c(15,100))
```



## Urban 0
```{r, fig.width=6, fig.height=3}
data <- select_data("urban_0", c(1,2,3,6), c(100, 15))

result <- customcluster(data, k=4, cluster_algo="PAM", dist_metric="CORT")
result <- tibble::rownames_to_column(result, "iso3")
do_all_plots(result, data, varnums=c(15,100))
```
  

## Urban 1    
```{r, fig.width=6, fig.height=3}
data <- select_data("urban_1", c(1,2,3,6), c(100, 15))

result <- customcluster(data, k=4, cluster_algo="PAM", dist_metric="CORT")
result <- tibble::rownames_to_column(result, "iso3")
do_all_plots(result, data, varnums=c(15,100))
```


# MTS clustering with custom aglo (all variables)

```{r}
# retrieve list of all variable numbers
datatemp <- read.csv(file="./data/data_all_999.csv")
varnums <- unique(datatemp$varnum)
varnums
```

```{r}
length(varnums)
```

```{r}
data <- select_data("all_999", c(1,2,3,6), varnums)

result <- customcluster(data, k=4, cluster_algo="PAM")

result <- tibble::rownames_to_column(result, "iso3")
result
```

```{r}
do_all_plots(result, data, varnums=c(15,100))
```

```{r}
write.csv(result, paste(DIR, "full_mts_custom_clusters.csv", sep=""), row.names = FALSE)
```

## Try k=6 for MTS

# MTS clustering with custom aglo (all variables)

```{r}
data <- select_data("all_999", c(1,2,3,6), varnums)

result <- customcluster(data, k=6, cluster_algo="PAM")

result <- tibble::rownames_to_column(result, "iso3")
result
```

```{r}
do_all_plots(result, data, varnums=c(15,100))
```

add cluster info to TS data

```{r}
data2 <- data[data$varnum==15,]

data2$cluster <- FALSE

for (row in 1:nrow(result)) {
  # print(result[row,]$iso3)
  data2[data2$iso3==(result[row,]$iso3),]$cluster <- result[row,]$result
}
```

## Visualise Clusters

```{r}
table(result$result)
```

```{r}
# plot_lines <- function(df) {
#   ggplot(data=df, aes(x=year, y=median, group=iso3, colour=as.factor(cluster))) + # colour=iso3 could make color income group
#   geom_line(alpha=0.2) +
#   guides(colour = guide_legend(override.aes =  = list(alpha = 1)))
# }
# 
# plot_lines(data2)
```

seperate plots

```{r}
# plot_lines <- function(df) {
#   ggplot(data=df, aes(x=year, y=median, group=iso3, color=as.factor(cluster))) + # colour=iso3 could make color income group
#   geom_line(alpha=0.2) +
#   ylim(0,1200) +
#   scale_color_manual(values=c("#000000", "#000000"))
# 
#   # guides(color = guide_legend(override.aes = list(alpha = 1)))
# }
# 
# for (i in 1:6) {
#   print(plot_lines(data2[data2$cluster==i,]))
# }
```

```{r}
plot_map(result)
```

```{r}
write.csv(result, paste(DIR, "full_mts_custom_clusters_k_6.csv", sep=""), row.names = FALSE)
```

# Investigate income 7

```{r}
data <- select_data("all_999", c(7), c(15))
data
```

# Explore custom cluster other metrics

```{r}
data <- select_data("all_999", c(1,6), c(100, "15"))

result <- customcluster(data, k=2, cluster_algo="PAM", dist_metric="CORT")

stats <- get_results(result$result, result$income)
stats
```

# plot incomes
```{r}
data <- select_data("all_999", c(1,2,3,6), c(15))
plot_lines(data, colour_col = "income", yaxis="Median sugar-sweetened\nbeverage intake (g/day)", key_title="Income Class")

```

